Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2023-08-10 unimodular-covers-CombTheory-final.tex
corrected repeated label

\begin{claim}
%\paco{new claim. Note I changed the roles of $r'$ and $r''$, since (the new) $r''$ is only used inside the claim}
\label{claim:r}
$r'$ has at least the same length as $r$. 
\end{claim}

@@

\begin{itemize}
\item \underline{$f_p(q_1+q_2-p_1)> 0$}. In this case the line containing $r$ and $r'$ separates $p$ from  $q_1+q_2-p_1$.
This implies
\[
f_q(r'_2) < f_q(q_1+q_2-p_1) = 1, \quad f_q(r'_1) > f_q(p_1) =-1,
\]
while Claims~\ref{claim:r} and~\ref{claim:width} imply that $\width_{f_q}(r')\ge \width_{f_q}(r)  \ge w\ge 2$.

\item \underline{$f_p(q_1+q_2-p_1)\le 0$}.
We observe that $g(r_2) - g(r_1)$ is positive (and integer) because $r$ has positive slope and separates $p_1$ from $q_2$. But Claim~\ref{claim:r} gives
\[
g(r_2) - g(r_1) \le g(r'_2) - g(r'_1) 
\]
which is in this case strictly smaller than $g(q_1+q_2-p_1) - g(p_1) =1$.
\qedhere
\end{itemize}
\end{proof}

>>>>

\begin{claim}
%\paco{new claim. Note I changed the roles of $r'$ and $r''$, since (the new) $r''$ is only used inside the claim}
\label{claim:r2}
$r'$ has at least the same length as $r$. 
\end{claim}

@@

\begin{itemize}
\item \underline{$f_p(q_1+q_2-p_1)> 0$}. In this case the line containing $r$ and $r'$ separates $p$ from  $q_1+q_2-p_1$.
This implies
\[
f_q(r'_2) < f_q(q_1+q_2-p_1) = 1, \quad f_q(r'_1) > f_q(p_1) =-1,
\]
while Claims~\ref{claim:r2} and~\ref{claim:width} imply that $\width_{f_q}(r')\ge \width_{f_q}(r)  \ge w\ge 2$.

\item \underline{$f_p(q_1+q_2-p_1)\le 0$}.
We observe that $g(r_2) - g(r_1)$ is positive (and integer) because $r$ has positive slope and separates $p_1$ from $q_2$. But Claim~\ref{claim:r2} gives
\[
g(r_2) - g(r_1) \le g(r'_2) - g(r'_1) 
\]
which is in this case strictly smaller than $g(q_1+q_2-p_1) - g(p_1) =1$.
\qedhere
\end{itemize}
\end{proof}
